Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
wip

@@

The algorithm in this section and the algorithm for $k=3$ (cf. Section~\ref{sec:k3}) are modified versions of the algorithm DET from \cite{repartition-disc}.
The difference is in the choice of partition after a component merge.
In DET, the partition was arbitrary.
In the algorithm for the learning model, we choose the partition closest to the initial partition.
\maciek{component respecting?}
In the algorithm from Section~\ref{sec:k3}, we choose the partition closest to the current partition (a repartition of minimum cost).

@@

\begin{theorem}	\label{thm:upperbound}
	\PPL reaches the final partition $P_F$
	 and it is $(2\cdot (k-1)\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
	On each inter-cluster request,
	the algorithm enumerates all \maciek{component-respecting} $\ell$-way partitions of components
	that are in the same (closest) distance to $P_I$.
	That is, 
	once it reaches a partition $P$ at distance $\Delta^* = \Delta(P)$,
	it does not move to a partition
	$P', \Delta(P') > \Delta^*$,
	before it enumerates all partitions at distance $\Delta^*$.
	Therefore,
	\PPL eventually reaches  the partition $P_F$ at distance $\Delta^*=\OPT$.
	With each distinct request, 
	the size of some component increases by one.
	For any cluster $F_i \in P_F$,
	we have $\sum_{C \in F_i} |C| = k$.
	A component $C \in F_i$,
	 initially begins as an isolated node and it grows by gaining $|C|-1$ more nodes.
	Hence, the total number of times a component in $F_i$ grows is 
	$\sum_{C \in F_i} (|C|-1) \leq k-1$.
	Therefore, there are at most  $(k-1)\cdot\ell $ distinct requests
	for which \PPL performs a repartitioning.
	I.e.,
	 \PPL performs at most $(k-1)\cdot\ell $ repartitions.
	By Lemma \ref{lemma:rebalancecost},
	each repartitioning costs at most $2\cdot\OPT$.
	The total cost is therefore at most $2\cdot\OPT\cdot (k-1) \cdot\ell$, which implies the competitive ratio.
\end{proof}

>>>>

The algorithm in this section and the algorithm for $k=3$ (cf. Section~\ref{sec:k3}) are modified versions of the algorithm DET from \cite{repartition-disc}.
The difference is in the choice of partition after a component merge.
In DET, the partition was arbitrary.
In the algorithm for the learning model, we choose the \maciek{component respecting?} partition closest to the initial partition.
In the algorithm from Section~\ref{sec:k3}, we choose the partition closest to the current partition (a repartition of minimum cost).

@@

@@

\begin{theorem}	\label{thm:upperbound}
	\PPL reaches the final partition $P_F$
	 and it is $(2\cdot (k-1)\cdot\ell)$-competitive.
\end{theorem}
\begin{proof}
	On each inter-cluster request,
	the algorithm enumerates all \maciek{component-respecting} $\ell$-way partitions of components
	that are in the same (closest) distance to $P_I$.
	That is, 
	once it reaches a partition $P$ at distance $\Delta^* = \Delta(P)$,
	it does not move to a partition
	$P', \Delta(P') > \Delta^*$,
	before it enumerates all partitions at distance $\Delta^*$.
	Therefore,
	\PPL eventually reaches  the partition $P_F$ at distance $\Delta^*=\OPT$.
	With each distinct request, 
	the size of some component increases by one.
	For any cluster $F_i \in P_F$,
	we have $\sum_{C \in F_i} |C| = k$.
	A component $C \in F_i$,
	 initially begins as an isolated node and it grows by gaining $|C|-1$ more nodes.
	Hence, the total number of times a component in $F_i$ grows is 
	$\sum_{C \in F_i} (|C|-1) \leq k-1$.
	Therefore, there are at most  $(k-1)\cdot\ell $ distinct requests
	for which \PPL performs a repartitioning and
	 \PPL performs at most $(k-1)\cdot\ell $ repartitions.
	By Lemma \ref{lemma:rebalancecost},
	each repartitioning costs at most $2\cdot\OPT$.
	The total cost is therefore at most $2\cdot\OPT\cdot (k-1) \cdot\ell$, which implies the competitive ratio.
\end{proof}
